Estimating Information Transfer from Different Data Sources via Precise Bias-variance Asymptotics

### 2021-07-11 revision_journal/results.tex
wip

\begin{theorem}[Variance asymptotics under covariate shift]\label{thm_main_RMT}
Under Assumption \ref{assm_big1} (recalling $\varphi > 4$), for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
	\begin{align}\label{lem_cov_shift_eq}
		\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{\alpha_1 a^2\cdot M^\top M + \alpha_2}  }}
		\le \frac{(n_1+n_2)^{\frac 2{\varphi} - \frac 1 2 + c}}{p^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2},
	\end{align}
	uniformly in all $a\in \R$. Here $(\alpha_1, \alpha_2)$ is the solution of the following system of equations
	\begin{align}
		\alpha_1 + \alpha_2 = 1- \frac{p}{n_1 + n_2}, \quad
		\alpha_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{(a \lambda_i)^2 \alpha_1}{(a \lambda_i)^2 \alpha_1 + \alpha_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
	\end{align}
\end{theorem}
\todo{changed $a_1, a_2$ to $\alpha_1, \alpha_2$ since they conflict with $a$}

@@

\begin{proposition}\label{prop_main_RMT}
%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
			\begin{align}
				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
			\end{align}
%			\begin{align}\label{lem_cov_derv_eq}
%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
%			\end{align}
				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
		\be  \label{eq_a34extra}
		\begin{split}
				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{split}
			\ee
			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
\end{proposition}

>>>>

\begin{theorem}[Variance estimates under covariate shift]\label{thm_main_RMT}
Under Assumption \ref{assm_big1} (recalling $\varphi > 4$), for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
	\begin{align}\label{lem_cov_shift_eq}
		\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{\alpha_1 a^2\cdot M^\top M + \alpha_2}  }}
		\le \frac{(n_1+n_2)^{\frac 2{\varphi} - \frac 1 2 + c}}{p^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2},
	\end{align}
	uniformly in all $a\in \R$. Here $(\alpha_1, \alpha_2)$ is the solution of the following system of equations
	\begin{align}
		\alpha_1 + \alpha_2 = 1- \frac{p}{n_1 + n_2}, \quad
		\alpha_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{(a \lambda_i)^2 \alpha_1}{(a \lambda_i)^2 \alpha_1 + \alpha_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
	\end{align}
\end{theorem}
\todo{changed $a_1, a_2$ to $\alpha_1, \alpha_2$ since they conflict with $a$}

@@

\begin{theorem}[Bias estimates under covariate and model shift]\label{prop_main_RMT}
%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
			\begin{align}
				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
			\end{align}
%			\begin{align}\label{lem_cov_derv_eq}
%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
%			\end{align}
				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
		\be  \label{eq_a34extra}
		\begin{split}
				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{split}
			\ee
			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
\end{theorem}
